From textual to structured Web API Descriptions\\ \large Knowledge Discovery and Data Mining Seminar 2017

### 2017-08-29 Paper/Paper_KDD.tex
Algorithmen ueberarbeitet

\begin{algorithm}[H]
 \caption{Algorithm 1}
 \begin{algorithmic}[1]
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
 \REQUIRE word-vectors of the APIs
 \ENSURE  Correlation matrix
 \\ \textit{Procedure} :
  \STATE Calculate for each API combination s1 and s2
 \STATE Accumulate the to a correlation matrix
% als inspiration ;)
 %\\ \textit{LOOP Process}
  %\FOR {$i = l-2$ to $0$}
  %\STATE statements..
  %\IF {($i \ne 0$)}
  %\STATE statement..
  %\ENDIF
  %\ENDFOR
 %\RETURN $P$
 \end{algorithmic}
 \end{algorithm}

@@

\subsection{Density-Based Clustering}
The first clustering algorithm we tried out was the density-based spatial clustering of applications with noise (DBSCAN). DBSCAN is a density based clustering algorithm grouping together closely packed data-points with a given number of neighbours required for a point to be dense (minPts) and a maximum distance between two neighbours in a cluster $(\epsilon)$.

\begin{algorithm}[H]
 \caption{Algorithm 2}
 \begin{algorithmic}[1]
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
 \REQUIRE given number of neighbours required for a point to be dense, maximum distance between two
neighbours in a cluster, word-vectors of the APIs
 \ENSURE  Clusters with associated APIs
 \\ \textit{Procedure} :
  \STATE Arbitrarily choose an initial API $s_1$
 \STATE Mark s 1 and calculate the number of neighbours N in the distance ε
%...
% Das musst du irgendwie noch geschickter darstellen
 \end{algorithmic}
 \end{algorithm}

@@

\subsection{K-Means Clustering}
The clustering algorithm we used for our final implementation is k-means, one of the most widely used clustering algorithm. For a given set of data-points in a n-dimensional space Rn and an integer k the algorithm determines k points, called centres, minimizing the sum of the mean square distance from the data points to their nearest centre. We are using the k-means adaptation of the Lloyed-algorithm described in Algorithm 3.

\begin{algorithm}[H]
 \caption{Algorithm 3}
 \begin{algorithmic}[1]
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
 \REQUIRE Integer k, word-vectors of the APIs
 \ENSURE  k centres
 \\ \textit{Procedure} :
  \STATE Arbitrarily choose an initial k centres $C = {c_1, c_2, ..., c_k}$.
 \STATE For each $i \in {1, ..., k}$, set the cluster Ci to be the set of points in X that are closer to $c_i$ than
they are to $c_j~for ~all ~j ~6= i$.
\STATE For each $i \in {1, . . . , k}$, set $c_i$ to be the centre of mass of all points in $C_i : c_i = 1 |C_i| P x \in C_i x$.
\STATE Repeat Steps 2 and 3 until C no longer changes % Das kann man auch als Loop schreiben

 \end{algorithmic}
 \end{algorithm}

>>>>

\begin{algorithm}[H]
 \caption{Algorithm 1}
 \begin{algorithmic}[1]
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
 \REQUIRE word-vectors of the APIs
 \ENSURE  Correlation matrix
 \\ \textit{Procedure} :
\FOR {$\forall s_1 \in API$}
\FOR {$\forall s_2 \in API$} 
\STATE \begin{equation*}{Sim}_{con}\left(s_1,s_2\right)=\frac{\sum_{\epsilon\ {con}_{s1}}\sum_{w_j\epsilon\ {con}_{s2}}{sim(w_i,\ w_j)}}{\left|{con}_{s1}\right|\times\left|{con}_{s2}\right|} \end{equation*}
\ENDFOR
\ENDFOR
 \STATE Accumulate the to a correlation matrix
% als inspiration ;)
 %\\ \textit{LOOP Process}
  %\FOR {$i = l-2$ to $0$}
  %\STATE statements..
  %\IF {($i \ne 0$)}
  %\STATE statement..
  %\ENDIF
  %\ENDFOR
 %\RETURN $P$
 \end{algorithmic}
 \end{algorithm}

\begin{table}
\begin{tabular}{lll}
\hline
tester & test \\
\end{tabular}
\end{table}

@@

\subsection{Density-Based Clustering}
The first clustering algorithm we tried out was the density-based spatial clustering of applications with noise (DBSCAN). DBSCAN\cite{kanungo2002efficient} is a density based clustering algorithm grouping together closely packed data-points with a given number of neighbours required for a point to be dense (minPts) and a maximum distance between two neighbours in a cluster $(\epsilon)$.

\begin{algorithm}[H]
 \caption{Algorithm 2}
 \begin{algorithmic}[1]
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
 \REQUIRE given number of neighbours required for a point to be dense, \newline maximum distance between two
neighbours in a cluster, \newline word-vectors of the APIs
 \ENSURE  Clusters with associated APIs
 \\ \textit{Procedure} :
  \STATE Arbitrarily choose an initial API $s_1$
 \STATE 
%...
% Das musst du irgendwie noch geschickter darstellen
 \end{algorithmic}
 \end{algorithm}

@@

\subsection{K-Means Clustering}
The clustering algorithm we used for our final implementation is k-means, one of the most widely used clustering algorithm. For a given set of data-points in a n-dimensional space Rn and an integer k the algorithm determines k points, called centres, minimizing the sum of the mean square distance from the data points to their nearest centre. We are using the k-means adaptation of the Lloyed-algorithm described in Algorithm 3\cite{kanungo2002efficient}.

\begin{algorithm}[H]
 \caption{Algorithm 3}
 \begin{algorithmic}[1]
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
 \REQUIRE Integer k, \newline word-vectors of the APIs $W={w_1, w_1, ... w_n}$
 \ENSURE  k centres
 \\ \textit{Procedure} :
  \STATE Arbitrarily choose an initial k centres $C = {c_1, c_2, ..., c_k}$.
 \STATE Repeat \newline
\noindent\hspace*{5mm}%		    
			Assign each item $w_i$ to the cluster which has \newline 
\noindent\hspace*{5mm}%
			the closest cetroid;\newline
\noindent\hspace*{5mm}%
			Calculate new mean for each cluster;\newline
\newline
	Until convergence criteria is met.
 \end{algorithmic}
 \end{algorithm}
